I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-12-05 paper_io_sim.tex

		The explosive development of Big Data era seen in recent years results in 
		growing needs in data storing, data analysis. 
		Although large computing systems with powerful computing capability 
		have been increasingly used to process big datasets, there is still a bottleneck 
		in disk I/O. 
		Memory page cache is a solution applied to minimize disk accesses and 
		improve the I/O performance. 
		Despite of the fact that simulation tools for HPC have been developed to 
		support studies in computing systems optimization, page cache simulation 
		has not been fully captured, or absent in these simulators. 
		The lack of ability to simulate I/O with page cache leads to inaccurate 
		simulation results in many situations, especially in data intensive applications.

		In this paper, we propose a I/O simulation model with key features of the page cache.
		The model consists of simulation algorithms of I/O, main components 
		and mechanisms of page cache.
		We also implement the model with SimGrid, a simulation framework for 
		distributed systems, using WRENCH, a SimGrid-based workflow simulator. 
		Then we create simulators for applications in single-threaded, multi-threaded,
		network file system and neuroimaging usecases.
		Finally, we analyze the results, compare to the results of base-line WRENCH 
		simulator as well as real execution.
		The results show that our simulator not only achieves higher accuracy than 
		original WRENCH, but also simulates well the status of memory and 
		page cache during I/O operations. 
		Through this study, our effort is to contribute an analytical model 
		of the page cache, which can also be integrated to other simulators 
		to improve I/O simulation accuracy, with its practical results.

>>>>

		The rapid emergence of Big Data seen in recent years has resulted in a 
		growing needs for efficient data storing and optimized data analysis. 
		Despite relying on large computing infrastructures with powerful computing capability 
		to process these large datasets, an I/O bottleneck remains. 
        One widely-used approach to minimize the costs of data transfers during
        regular use is through the employment of the page cache.
		While many simulation tools have been developed to 
		support studies in computing systems optimization, page cache simulation 
		has not been fully captured or remains absent from these simulators. 
		The lack of ability to simulate I/O with page cache leads to inaccurate 
		simulation results in many situations, especially when dealing with data intensive applications.

		In this paper, we propose a I/O simulation model that characterizes the key features of the page cache.
		We have implemented the model with SimGrid, a simulation framework for 
		distributed systems, using WRENCH, a SimGrid-based workflow simulator. 
        Our simulator is compatible with both single-threaded and multithreaded applications,
        and can simulate both writeback and writethrough cache that can factor into local
        and network-based filesystems.
		The results show that our simulator not only achieves higher accuracy than 
		original WRENCH, but also effectively simulates memory contents and 
		page cache during I/O operations. 
		Through this study, our effort is to contribute an analytical model 
		of the page cache, which can also be integrated to other simulators 
		to improve I/O simulation accuracy, with its practical results.
